Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-01 doc/JFLA2022/paper.tex
Improve / expand presentation of Coq-community.

\emph{Coq-community} is an informal organization run by volunteer Coq users with objectives to maintain interesting Coq projects on the long-term and help Coq users to collaborate on documentation, tooling, etc.
%
It was created in 2018, inspired by the \emph{Elm Community} organization~\cite{zimmermann:tel-02451322}, and in fact such ``Community Package Maintenance Organizations'' exist in many ecosystems~\cite{zimmermann2021grounded}.
%
Today, it hosts over 50 projects maintained by over 30 maintainers.

>>>>

\emph{Coq-community} is an informal organization run by volunteer Coq users with objectives to maintain interesting Coq projects in the long-term and help Coq users to collaborate on documentation, tooling, etc.

It was created in 2018, inspired by the \emph{Elm Community} organization~\cite{zimmermann:tel-02451322}.
%
Such ``Community Package Maintenance Organizations'' actually exist in many ecosystems as they avoid the very common problem of an important package becoming unmaintained as its author has moved on or disappeared~\cite{zimmermann2021grounded}.

In the case of Coq, this problem may be even more prevalent as many packages are created by PhD students, or by researchers for a specific paper, but their authors do not intend to maintain the package in the long-term.
%
The authors are however generally very open to having someone else who expresses interest in their work continue the maintenance.
%
\emph{Coq-community} makes that easy by providing a process for transferring or forking an unmaintained package, tooling for setting up good maintenance practices (such as continuous integration) and by making it possible for someone to take over a package without committing in the long-term (as maintainers who drop out can easily be replaced by some other volunteers).
%
Today, \emph{Coq-community} hosts over 50 projects maintained by over 30 maintainers.
